---
title:  "Title of my presentation and the topic of today"
subtitle: "The subtitle (optional)"
author: 
  - "My name"
  - "MSc / MPhil / PhD Student: XXX"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: ['glasgow_light.css','image_title.css','outline.css','blockquote.css','text_color.css']
    seal: false
    nature:
      slideNumberFormat: "%current%"
      highlightStyle: github
      highlightLines: true
      ratio: 16:9
      countIncrementalSlides: true
      
---

class: title-slide

# This is my title: An Excellent Presentation

## AATS Annual Meeting 2021 

### Dr. XYZ

###Associate Professor of xxxx

###University of xxxx

###xxxx, xxxx

###`r icon::ii("email")` abc@123.edu  

---

# Contents of the title slide

* The title slide contains information from the yaml. The **yaml** is first part of the Rmarkdown document before the body of the document.

* The yaml options for **xaringan** slides provided in this template are title, author, and date. 

* Apart from the standard yaml options, **autoplay** and **loop** can be used to loop the slides creating a continuous slideshow.

* the yaml contains .text-rust[_seal:false_], that way, you can create a new title slide without pulling information from the yaml.

---
class: center, middle, chapter



# Using this Template

---

# Using this Template

Details regarding using the xaringan library and this template is available at 

* (https://bookdown.org/yihui/rmarkdown/xaringan.html)
This is a link to the chapter on the **xaringan** library.

* (https://slides.yihui.org/xaringan/#1) This is a link to the official documentation on **xaringan**.

* (https://github.com/yihui/xaringan/wiki) This is a link to the **xaringan** wiki page. It provides tips regarding use as well as further customisation.

* (https://github.com/gnab/remark/wiki) The **remark.js** wiki is a good tool to learn how to make slides.


---
# Layout 

* Simple title, bullet, text layout 

* Two column with equal column layout 

* Two column with side-bar and content layout 

---

# One bullet point at a time

* First point

--

* Second point 

--

* Third point 

---



# Insert graphs


```{r, echo=FALSE,warning=FALSE,message=FALSE}

library(ggplot2)
library(extrafont)
loadfonts(device = "win")


```


```{r,echo=FALSE,warning=FALSE,message=FALSE}

##################################################################
##                     UofG graphical theme                     ##
##################################################################


# This theme is created using the U of G branding guidelines.
# Detailed guidance can be found here - https://www.gla.ac.uk/myglasgow/staff/brandtoolkit/
# Fonts: 
# Swiss 721 and Adobe Garamond are the recommended fonts. However, both these fonts
# are proprietary. Thus, for routine use, both Arial and TNR are acceptable.
# The theme is a modification of the minimal theme. 
# Title = U of G blue
# subtitle = U of G burgundy
# footnotes  = black
# The axes labels and tick labels are in Arial.
# The plot background is U of G 30% slate.
# Theme loads the Titillium font from google fonts using the # showtext library; the yarrr library is needed for the 
# creating the transparent gray background for the plot.

# define colors for the U of G branding.

gla_blue <- rgb(0/255,56/255,101/255)
gla_heather <- rgb(91/255,83/255,125/255)
gla_aquamarine <- rgb(154/255,185/255,173/255)
gla_slate <- rgb(79/255,89/255,97/255)
gla_rose <-  rgb(210/255,120/255,171/255)
gla_mocha <- rgb(181/255,144/255,121/255)
gla_lawn <- rgb(132/255,189/255,80/255)
gla_cobalt <- rgb(0/255,117/255,176/255)
gla_turquiose <- rgb(0/255,181/255,209/255)
gla_sunshine <- rgb(255/255,220/255,54/255)
gla_pumpkin <- rgb(244/255,185/255,72/255)
gla_thistle <- rgb(149/255,18/255,114/255)
gla_pillarbox <- rgb(213/255,0/255,50/255)
gla_lavender <- rgb(91/255,77/255,148/255)
gla_forest <- rgb(0/255,81/255,51/255)
gla_burgundy <- rgb(125/255,34/255,57/255)
gla_rust <- rgb(154/255,58/255,6/255)
gla_sandstone <- rgb(82/255,71/255,59/255)


gla <- c(gla_blue, 
         gla_rust,
         gla_aquamarine,
         gla_sandstone,
         gla_pumpkin)

twoc <- c(gla_burgundy, gla_cobalt)



theme_gla <- function(){ 
  
  library(yarrr)
 
  # use the minimal theme as it has the best appearance.
  # would like to add a very light grey background to the graph.
  theme_minimal() %+replace%    #replace elements we want to change
    
    
    theme(
      
      # add very light gray background.
      
      panel.background =   
        element_rect(fill = yarrr::transparent("#f7f7f7",0.1), colour = NA),
      
      #grid elements
      panel.grid.major = element_blank(),    #strip major grid lines
      panel.grid.minor = element_blank(),    #strip minor grid lines
      axis.ticks = element_blank(),          #strip axis ticks
      
      #since theme_minimal() already strips axis lines, 
      #we don't need to do that again
      
      #text elements
      plot.title = element_text(             #title
        family = 'Arial',            #set font family
        size = 30,                #set font size
        face = 'bold',            #bold typeface
        hjust = 0,                #left align
        vjust = 2,
        colour = gla_blue),               #raise slightly
      
      plot.subtitle = element_text(          #subtitle
        family = 'Arial',            #font family
        size = 15,
        face = "italic",
        hjust = 0,
        color = gla_burgundy),               #font size
      
      plot.caption = element_text(           #caption
        family = 'Arial',            #font family
        size = 8,                 #font size
        hjust = 1,
        face = "italic"),                #right align
      
      axis.title = element_text(         #axis titles
        family = "Arial",                   #font family
        size = 10),                      #font size
      
      axis.text = element_text(              #axis text
        family = "Arial",            #axis famuly
        size = 10),                #font size
      
      axis.text.x = element_text(   #margin for axis text
        margin=margin(5, b = 10)),
      
      legend.title = element_text(
        family = "Arial",
        size = 15),
      
      legend.text = element_text(
        family = "Arial",
        size = 10)
      
      #since the legend often requires manual tweaking 
      #based on plot content, don't define it here
    )
  
}

```


```{r, echo = FALSE, warning=FALSE,message=FALSE,fig.height=6,fig.width=11, ,fig.align='center'}



library(ggthemes)
library(tidyverse)
library(survival) #<<
library(GGally) #<<

s <- survfit(Surv(time, status) ~ sex, data = lung)

GGally::ggsurv(s,CI = T,plot.cens = T) + theme_gla() + scale_color_manual(values = gla) + labs(title = "Survival curve",
                                                                                               subtitle = "Glasgow colors")


```

---

# Highlight code

* Code can be highlighted using **#<<** 

* Use [ some R code ] to allow for vertical scrolling of R chunk and results.

.pre-large[

```{r}

# use .pre[some R code] to allow for vertical scrolling of R code chunk


a <- lm(mpg ~ hp, data = mtcars) 

summary(a) #<<
```
]

---

# Whole slide scroll 

.pre-whole[

```{r}

s <- survfit(Surv(time, status) ~ sex, data = lung)

summary(s)

```
]

---

# Two column layout

.pull-right[

* Some points 

* More points

* Even more points 

* The slide is divided into 2 equal parts and text, bullet points, or images can be pasted in either one
]

.pull-left[

![](https://d33wubrfki0l68.cloudfront.net/62bcc8535a06077094ca3c29c383e37ad7334311/a263f/assets/img/logo.svg)

* the image

* another image
]


---

# GGplot2 graphs

.pull-right[

```{r, fig.height=5,fig.width=8}

ggplot(mtcars, aes(x = mpg, y = hp, color = factor(gear))) + geom_point() +  scale_color_manual(values = gla) + theme_gla()

```

]

.pull-left[

* ggplot2 graphs can also be placed in the half column
]

---

# Context boxes


.content-box-blue[This is point 1]

--

.content-box-green[This is point 2]

--

.content-box-army[This is point 3]

--

.blockquote[- Latex is dead, long live CSS

- More information ]

---

# Change text colors

* Using text colors css, we can change the text colors.

.text-cobalt[Blue colored text]

--

.text-thistle[Thistle colored text]

--

## .text-rust[Rust colored text] - This is a 2nd level header 

--

.text-moss[Moss colored text]

--

* To change the color of italic font

_.text-thistle[some thistle colored italic font]_


---

# Animated Graphs 

* Animated graphs and interactive graphs using plotly and gganimate can be embedded into slides 

